### 2017-02-15 main.tex
Response2 to the editor. A little argumentative, isn't it? Hmmm. Should fix that.
Added Nathan's birds to accuracy table. Fixed dataset size info. Minor wording changes.

Including diff.pdf

If precise moments in song can reliably be detected quickly enough to
trigger other apparatus during singing, then this consistency of
behaviour allows a variety of experiments.  A common area of study
with this song-triggering technique is the anterior forebrain pathway
(AFP), a homologue of mammalian basal ganglia consisting of a few
distinct brain areas concerned with the learning and production of
song.  For example, stimulation of the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song shows that this area
controls specific variables in song output \cite{Kao2005}.
Song-synchronised stimulation of LMAN and the high vocal centre (HVC)
in one hemisphere or the other showed that control of song rapidly
switches between hemispheres \cite{Wang2008interhemispheric}.
Feedback experiments have shown that Field L and the caudolateral
mesopallium may hold a representation of song against which auditory
signals are compared \cite{Keller2009}.  Renditions of a syllable that
were disrupted by white noise when they were slightly above (or below)
the syllable's average pitch showed that the apparently random natural
variability in songbird motor output is used to drive change in the
song \cite{Tumer2007pitchshift}. Furthermore, AFP produces a
corrective signal to bias song away from those disruptions
\cite{Andalman2009}. The
song change is isolated to within roughly 10 milliseconds (ms) of the
stimulus, and the shape of the learned response can be predicted by
a simple mechanism \cite{Charlesworth2011learning}.

AFP transfers the error signal to
the robust nucleus of the arcopallium (RA) using
NMDA-receptor--mediated glutamatergic transmission \cite{Warren2011}. By looking at song
recovery after applying the same pitch-shift paradigm,
the caudal medial nidopallium is
implicated in memorising or recalling a recent song target, but for
neither auditory processing nor directed motor learning \cite{Canopoli2014}.

@@

Data consisted of extracted, aligned songs, and additional song-length samples of non-song (cage noise, calls, other birds' song). These were divided into training and test sets. The sizes of our data sets are given in Table~\ref{table:datasizes}.

\begin{table}
  \begin{tabular}{c|cccc}
    Bird & Training songs & Test songs & Training non-song & Test non-song \\ \hline
    A & 1000 & 1818 & 1000 & 3636 \\
    B & 1000 & 1530 & 1428 & 2185 \\
    C & 1000 & 1245 & 990 & 1233 \\
    D & 1000 & 1614 &  & 247
  \end{tabular}
  \caption{Sizes of our training and test sets.}
  \label{table:datasizes}
\end{table}

@@

Because the data set consists of temporally aligned songs, the moment
at which detection should occur during each song sample is available
(albeit with minor variations due to the alignment process used
\cite{Poole2012}).  The detector can be checked by comparing its
response to the recorded training songs against these
``canonical'' detection events.  To this end, besides the trained
network object, our learning code produces an audio file consisting of
all of the training data on the left audio channel and a delta
function at each aligned moment of target syllable presentation on the
right channel. Thus, when played on any audio player, the left channel
may be provided as input to the detector, and the the detector's
output pulses may be compared against the right channel.

@@

\begin{table}
  \begin{tabular}{c|rr}
    Target time & \% True positives & \% False positives \\ \hline
    $t^*_1$ & 99.34 &  0.0015 \\
    $t^*_2$ & 99.65 &  0.00040 \\
    $t^*_3$ & 98.98 &  0.0015 \\
    $t^*_4$ & 99.30 &  0.00093 \\
    $t^*_5$ & 99.73 &  0.000094 \\
    $t^*_6$ & 98.31 &  0.0026
  \end{tabular}
  \caption{Mean values for the detection accuracies shown in \fig{fig:accuracies}.}
  \label{table:accuracies}
\end{table}

@@

%\bibliography{birds}
\begin{thebibliography}{10}

\bibitem{Kao2005}
Kao MH, Doupe AJ, Brainard MS.
\newblock Contributions of an avian basal ganglia--forebrain circuit to
  real-time modulation of song.
\newblock Letters to Nature. 2005 February;433:638--643.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v433/n7026/abs/nature03127.html}.

\bibitem{Wang2008interhemispheric}
Wang CZH, Herbst JA, Keller GB, Hahnloser RHR.
\newblock Rapid Interhemispheric Switching during Vocal Production in a
  Songbird.
\newblock PLOS Biology. 2008 October;6(10).
\newblock Available from:
  \url{http://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.0060250}.

\bibitem{Keller2009}
Keller GB, Hahnloser RHR.
\newblock Neural processing of auditory feedback during vocal practice in a
  songbird.
\newblock Nature. 2009 January;457:187--190.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v457/n7226/abs/nature07467.html}.

\bibitem{Tumer2007pitchshift}
Tumer EC, Brainard MS.
\newblock Performance variability enables adaptive plasticity of 'crystallized'
  adult birdsong.
\newblock Nature. 2007 December;450:1240--1244.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v450/n7173/abs/nature06390.html}.

\bibitem{Andalman2009}
Andalman AS, Fee MS.
\newblock A basal ganglia-forebrain circuit in the songbird biases motor output
  to avoid vocal errors.
\newblock Proceedings of the National Academy of Sciences of the United States
  of America. 2009 July;106(30):12518--12523.
\newblock Available from:
  \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2709669/}.

\bibitem{Charlesworth2011learning}
Charlesworth JD, Tumer EC, Warren TL, Brainard MS.
\newblock Learning the microstructure of successful behavior.
\newblock Nature Neuroscience. 2011;14(3):373--380.
\newblock Available from:
  \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3045469/}.

\bibitem{Warren2011}
Warren TL, Tumer EC, Charlesworth JD, Brainard MS.
\newblock Mechanisms and time course of vocal learning and consolidation in the
  adult songbird.
\newblock Journal of Neurophysiology. 2011 October;106(4):1806--1821.
\newblock Available from:
  \url{http://jn.physiology.org/content/106/4/1806.full}.

\bibitem{Canopoli2014}
Canopoli A, Herbst JA, Hahnloser RHR.
\newblock A Higher Sensory Brain Region Is Involved in Reversing
  Reinforcement-Induced Vocal Changes in a Songbird.
\newblock The Journal of Neuroscience. 2014;34(20):7018--7026.
\newblock Available from:
  \url{http://www.jneurosci.org/content/34/20/7018.full}.

\bibitem{Leonardo1999}
Leonardo A, Konishi M.
\newblock Decrystallization of adult birdsong by perturbation of auditory
  feedback.
\newblock Nature. 1999 June;399:466--470.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v399/n6735/abs/399466a0.html}.

\bibitem{Skocik2013}
Skocik M, Kozhevnikov A.
\newblock Real-time system for studies of the effects of acoustic feedback on
  animal vocalizations.
\newblock Frontiers in Neural Circuits. 2013 January;6(111).
\newblock Available from:
  \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3539774/}.

\bibitem{Poole2012}
Poole B, Markowitz JE, Gardner TJ.
\newblock The Song Must Go On: Resilience of the Songbird Vocal Motor Pathway.
\newblock PLOS One. 2012 June;7(6).
\newblock Available from:
  \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0038173}.

\bibitem{Tchernichovski2011SAP}
Tchernichovski O. Sound Analysis Pro User Manual; 2011.
\newblock Available from: \url{http://soundanalysispro.com/manual-1}.

\bibitem{Jacobsen2003SlidingDFT}
Jacobsen E, Lyons R.
\newblock The sliding DFT.
\newblock IEEE Signal Processing Magazine. 2003 Mar;20(2):74--80.
\newblock Available from:
  \url{http://www.cmlab.csie.ntu.edu.tw/DSPCourse/reference/Sliding\%20DFT.pdf}.

\bibitem{hkp}
Hertz JA, Krogh AS, Palmer RG.
\newblock Introduction to the Theory of Neural Computation.
\newblock Perseus Books; 1991.

\bibitem{Noll1970pitchdetection}
Noll AM.
\newblock Pitch determination of human speech by the harmonic product spectrum,
  the harmonic sum spectrum, and a maximum likelihood estimate.
\newblock In: Proceedings of the symposium on computer processing in
  communications. vol.~19; 1970. p. 779--797.

\end{thebibliography}

>>>>

If precise moments in song can reliably be detected quickly enough to
trigger other apparatus during singing, then this consistency of
behaviour allows a variety of experiments.  A common area of study
with this song-triggering technique is the anterior forebrain pathway
(AFP), a homologue of mammalian basal ganglia consisting of a few
distinct brain areas concerned with the learning and production of
song.  For example, stimulation of the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song shows that this area
controls specific variables in song output \cite{Kao2005}.
Song-synchronised stimulation of LMAN and the high vocal centre (HVC)
in one hemisphere or the other showed that control of song rapidly
switches between hemispheres \cite{Wang2008interhemispheric}.
Feedback experiments have shown that Field L and the caudolateral
mesopallium may hold a representation of song against which auditory
signals are compared \cite{Keller2009}.  Renditions of a syllable that
were disrupted by white noise when they were slightly above (or below)
the syllable's average pitch showed that the apparently random natural
variability in songbird motor output is used to drive change in the
song \cite{Tumer2007pitchshift}. Furthermore, AFP produces a
corrective signal to bias song away from those disruptions
\cite{Andalman2009}. The
song change is isolated to within roughly 10 milliseconds (ms) of the
stimulus, and the shape of the learned response can be predicted by
a simple mechanism \cite{Charlesworth2011learning}. AFP transfers the error signal to
the robust nucleus of the arcopallium (RA) using
NMDA-receptor--mediated glutamatergic transmission \cite{Warren2011}. By looking at song
recovery after applying the same pitch-shift paradigm,
the caudal medial nidopallium is
implicated in memorising or recalling a recent song target, but for
neither auditory processing nor directed motor learning \cite{Canopoli2014}.

@@

Data consisted of extracted, aligned songs, and additional song-length samples of non-song (cage noise, calls, other birds' song). These were divided into training and test sets. For Bird A, we used 1000 songs and 1000 non-song samples for training, and the remaining 1818 songs and 3636 nonsongs for testing. For birds B, C, and D, we used 1000 songs and 1000 non-songs for training, and another 1000 of each for testing.

%\begin{table}
% \begin{tabular}{c|cccc}
%    Bird & Training songs & Test songs & Training non-song & Test non-song \\ %\hline
 %   A & 1000 & 1818 & 1000 & 3636 \\
  %  B & 1000 & 1000 & 1000 & 1000 \\
 %   C & 1000 & 1000 & 1000 & 1000 \\
%    D & 1000 & 1000 &  1000 & 1000
%  \end{tabular}
%  \caption{Sizes of our training and test sets.}
%  \label{table:datasizes}
%\end{table}

@@

Because the data set consists of temporally aligned songs, the moment
at which detection should occur during each song sample is available
(albeit with minor variations due to the alignment process used
\cite{Poole2012}).  The detector can be checked by comparing its
response to the recorded training songs against these ``canonical''
detection events.  To this end, besides the trained network object,
our learning code produces an audio file consisting of all of the
training data on the left audio channel and a delta function at each
aligned moment of target syllable presentation on the right
channel. Thus, when played on any audio player, the left channel may
be provided as input to the detector, and the the detector's output
pulses may be compared against the ``ground truth'' given by the
canonical detection event provided by the right channel.

@@

\begin{table}
  \begin{tabular}{rc|rr}
    Bird & Target time & \% True positives & \% False positives \\ \hline
    A&$ t^*_1$ & 99.72 &  0.0025 \\
    &$ t^*_2$ & 99.81 &  0.00053 \\
    &$ t^*_3$ & 99.78 &  0.00062 \\
    &$ t^*_4$ & 99.69 &  0.00082 \\
    &$ t^*_5$ & 99.75 &  0.00028 \\
    &$ t^*_6$ & 99.54 &  0.0012 \\
    B&$ t^*$ & 99.37 & 0.0039 \\
    C&$ t^*$ & 99.13 & 0.0011 \\
    D&$ t^*$ & 99.34 &0.0026 \\
  \end{tabular}
  \caption{Mean values for the detection accuracies shown in \fig{fig:accuracies}.}
  \label{table:accuracies}
\end{table}

@@

\bibliography{birds}
